Constraints on the masses of substructures in $x$ lens galaxies

### 2016-11-15 doc/Paper2/ms.tex
Prior table

>>>>

\section{Prior Distribution}
The joint prior distribution for the hyperparameters, parameters, and the
data is summarised in Table~\ref{tab:priors}.

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Numbers of Blobs}\\
\hline
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
\hline
{\bf Source hyperparameters} ($\boldsymbol{\alpha}_{\rm src}$)\\
\hline
$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
$R_{\rm src}$   &	Typical distance of blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & LogUniform(0.01$\times${\tt imageWidth}, 10$\times${\tt imageWidth})\\
$\mu_{\rm src}$ &	Typical flux of source blobs	& $\ln(\mu_{\rm src}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
$W_{\rm max}^{\rm src}$ &		Maximum width of source blobs	& LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
$W_{\rm min}^{\rm src}$ &		Minimum width of source blobs	& Uniform(0, $W_{\rm max}^{\rm src}$)\\
\hline
{\bf Lens hyperparameters} ($\boldsymbol{\alpha}_{\rm lens}$)\\
\hline
$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
$R_{\rm lens}$  &	Typical distance of blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& LogUniform(0.01$\times${\tt imageWidth}, 10$\times${\tt imageWidth})\\
$\mu_{\rm lens}$&	Typical mass of lens blobs	& $\ln(\mu_{\rm lens}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
$W_{\rm max}^{\rm lens}$ &		Maximum width of lens blobs	& LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
$W_{\rm min}^{\rm lens}$ &		Minimum width of lens blobs	& Uniform(0, $W_{\rm max}^{\rm lens}$)\\
\hline
{\bf Source Blob Parameters} ($\boldsymbol{\theta}_i^{\rm src}$)\\
\hline
$(x_i^{\rm src}, y_i^{\rm src})$ & Blob position & Circular(location=$(x_c^{\rm src}, y_c^{\rm src})$, scale=$R_{\rm src}$)\\
$A_i$  & Blob flux & Exponential(mean=$\mu_{\rm src}$)\\
$w_i$  & Blob width & Uniform($W_{\rm min}^{\rm src}$, $W_{\rm max}^{\rm src}$)\\
\hline
{\bf Lens Blob Parameters} ($\boldsymbol{\theta}_i^{\rm lens}$)\\
\hline
$(x_i^{\rm lens}, y_i^{\rm lens})$ & Blob position & Circular(location=$(x_c^{\rm lens}, y_c^{\rm lens})$, scale=$R_{\rm lens}$) \\
$M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
$v_i$  & Blob width & Uniform($W_{\rm min}^{\rm lens}$, $W_{\rm max}^{\rm lens}$)\\
\hline
{\bf Smooth Lens Parameters} ($\boldsymbol{\theta}_{\rm SIE}$)\\
\hline
$b$ & SIE Einstein Radius & LogUniform(0.001$\times${\tt imageWidth}, {\tt imageWidth})\\
$q$ & Axis ratio & Uniform(0, 0.95)\\
$(x_c^{\rm SIE}, y_c^{\rm SIE})$ & Central position & iid Cauchy(location=$(0,0)$, scale=0.1$\times${\tt imageWidth})\\
$\theta$ & Orientation angle & Uniform$(0, \pi)$\\
$\gamma$ & External shear & Cauchy$(0, 0.05)T(0, \infty)$\\
$\theta_\gamma$ & External shear angle & Uniform$(0, \pi)$\\
\hline
{\bf Noise Parameters} ($\boldsymbol{\sigma}$)\\
\hline
$\sigma_0$ & Constant component of noise variance & $\ln(\sigma_0) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
$\sigma_1$ & Coefficient for variance increasing with flux &
$\ln(\sigma_1) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
\hline
{\bf Data} ($\boldsymbol{D}$)\\
\hline
$D_{ij}$ & Pixel intensities & Normal$(m_{ij}, s_{ij}^2 + \sigma_0^2 + \sigma_1m_{ij})$
\end{tabular}
\caption{The prior distribution for all hyperparameters, parameters, and the
data, in our model. Uniform$(a, b)$ is a uniform
distribution between $a$ and $b$. LogUniform$(a, b)$ is a log-uniform
distribution (with density $f(x) \propto 1/x$, sometimes erroneously called
a Jeffreys prior) between $a$ and $b$. The notation $T(\alpha, \beta)$ after
a distribution denotes truncation to the interval $[\alpha, \beta]$. The
constant {\tt imageWidth} is the geometric mean of the image dimensions in
the $x$ and $y$ directions. {\color{blue} THIS WILL NEED TO BE UPDATED}
\label{tab:priors}}
\end{table*}
